Example Manuscript Template for a Data Analysis Project

### 2025-03-14 products/manuscript/Manuscript.qmd
commit to all changes to the manuscript

The structure below is one possible setup for a manuscript, or a general data analysis project (including the course project). Adjust as needed. 
You don't need to have exactly these sections, but the content covering those sections should be addressed.

This uses MS Word as output format. [See here](https://quarto.org/docs/output-formats/ms-word.html) for more information. You can switch to other formats, like html or pdf. See [the Quarto documentation](https://quarto.org/) for other formats.

@@

1. College of Public Health, University of Georgia, Athens, GA, USA.
2. Another Affiliation, Athens, GA, USA.
3. Yet another Affiliation.

@@

$\land$ Corresponding author: some@email.com

@@

MADA PROJECT PART 1:

>>>>

@@

1. College of Public Health, University of Georgia, Athens, GA, USA.

@@

$\land$ Corresponding author: kelvinbwambale8@gmail.com

@@
